Measuring Perceptions and Preferences for Meritocracy

### 2023-02-02 Title Page.Rmd
ajustes submit

---
title: "Measuring Perceptions and Preferences for Meritocracy"
linestretch: '1.5'
output:
  bookdown::pdf_document2:
    template: null
    toc: false
    number_sections: false
geometry: margin=0.78in
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage[figurename=Fig.]{caption}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
fontsize: 12pt

@@

Juan Carlos Castillo, Department of Sociology, Universidad de Chile (
juancastillov@uchile.cl - [jc-castillo.com](https://juancarloscastillo.github.io/jc-castillo/) -  Ignacio Carrera Pinto 1045 Ñuñoa, Santiago de Chile )

@@

>>>>

---
title: "Measuring Perceptions and Preferences for Meritocracy [^*]"
linestretch: '1.5'
output:
  bookdown::pdf_document2:
    template: null
    toc: false
    number_sections: false
geometry: margin=0.78in
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage[figurename=Fig.]{caption}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
fontsize: 12pt

@@

Juan Carlos Castillo, Department of Sociology, Universidad de Chile *

@@

Word count: 8998

[^*]: Corresponding author (juancastillov@uchile.cl - [jc-castillo.com](https://juancarloscastillo.github.io/jc-castillo/) -  Ignacio Carrera Pinto 1045 Ñuñoa, Santiago de Chile). The authors recognize the support of ANID/FONDECYT grant 1160921 and of  the Center for Conflict and Social Cohesion Studies (COES)  grant ANID/FONDAP 1513009.

### 2023-02-02 paper-blinded.Rmd
ajustes submit

---
title: "Measuring Perceptions and Preferences for Meritocracy"
css: "custom.css"
linestretch: '2.0'
link-citations: yes
# author: "Juan Carlos Castillo, Julio Iturra, Luis Maldonado, Francisco Meneses & Jorge Atria <br><br>"
# abstract: "Economic and social inequalities have generated growing concerns and crises across contemporary societies. The belief in meritocracy has been suggested as one of the factors that explain the persistence of inequality, as it would legitimize economic disparities based on differences in effort and talent. Despite its wide use as a concept, empirical research on meritocracy is relatively novel and characterized by diverse conceptualizations and measures that make the findings and their interpretation rather inconsistent. Most of the studies in the area have relied upon secondary data from different surveys to operationalize meritocracy, with a wide variation in the use and interpretation of the same measuring items. Based on a critical analysis of concepts and operationalizations of meritocracy in survey research, we propose a conceptual and measurement framework for perceptions and preferences for meritocracy and non-meritocracy in a minimalistic version (few items as possible), in order to be considered in comparative survey research studies. The proposal is first tested through confirmatory factor analysis (CFA) using available ISSP (International Social Survey Programme) inequality module items. Based on these results, in a second study we propose an  improved scale that better suits the perceptions/preferences distinction and that is tested  in a Chilean sample (N=2,141). The results of the CFA estimation give evidence of a better fit for the new scale. Our discussion highlights the importance of considering different dimensions in the study of meritocracy, both conceptually and empirically."
output:
  bookdown::pdf_document2:
     template: null
     toc: false
     number_sections: false
     keep_text: true
  # bookdown::word_document2:
  #   number_sections: false
  # bookdown::html_document2:
  #   number_sections: false
linkcolor: blue
bibliography:
  - input/bib/meritocracy.bib
csl: input/bib/asa6.csl
editor_options:
  chunk_output_type: console
geometry: margin=1in
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
#  - \usepackage[figurename=Fig.]{caption}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
always_allow_html: true # for word output
fontsize: 12pt
papersize: a4
---

```{r eval=FALSE, include=FALSE}
 # for render in pdf run rmarkdown::render_site("docs/paper.Rmd", output_format = "all")
 # clean #in the yml
 rmarkdown::render("paper-blinded.Rmd", output_format = "bookdown::pdf_document2")
 rmarkdown::render("paper-blinded.Rmd", output_format = "bookdown::html_document2")
 # rmarkdown::render("paper.Rmd", output_format = "bookdown::word_document2")
```

>>>>

---
title: "Measuring Perceptions and Preferences for Meritocracy"
css: "custom.css"
linestretch: '2.0'
link-citations: yes
# author: "Juan Carlos Castillo, Julio Iturra, Luis Maldonado, Francisco Meneses & Jorge Atria <br><br>"
# abstract: "Economic and social inequalities have generated growing concerns and crises across contemporary societies. The belief in meritocracy has been suggested as one of the factors that explain the persistence of inequality, as it would legitimize economic disparities based on differences in effort and talent. Despite its wide use as a concept, empirical research on meritocracy is relatively novel and characterized by diverse conceptualizations and measures that make the findings and their interpretation rather inconsistent. Most of the studies in the area have relied upon secondary data from different surveys to operationalize meritocracy, with a wide variation in the use and interpretation of the same measuring items. Based on a critical analysis of concepts and operationalizations of meritocracy in survey research, we propose a conceptual and measurement framework for perceptions and preferences for meritocracy and non-meritocracy in a minimalistic version (few items as possible), in order to be considered in comparative survey research studies. The proposal is first tested through confirmatory factor analysis (CFA) using available ISSP (International Social Survey Programme) inequality module items. Based on these results, in a second study we propose an  improved scale that better suits the perceptions/preferences distinction and that is tested  in a Chilean sample (N=2,141). The results of the CFA estimation give evidence of a better fit for the new scale. Our discussion highlights the importance of considering different dimensions in the study of meritocracy, both conceptually and empirically."
output:
  bookdown::pdf_document2:
     template: null
     toc: false
     number_sections: false
     keep_text: true
  bookdown::word_document2:
    number_sections: false
  bookdown::html_document2:
    number_sections: false
linkcolor: blue
bibliography:
  - input/bib/meritocracy.bib
csl: input/bib/asa6.csl
editor_options:
  chunk_output_type: console
geometry: margin=1in
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
#  - \usepackage[figurename=Fig.]{caption}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
always_allow_html: true # for word output
fontsize: 12pt
papersize: a4
---

```{r eval=FALSE, include=FALSE}
 # for render in pdf run rmarkdown::render_site("docs/paper.Rmd", output_format = "all")
 # clean #in the yml
 rmarkdown::render("paper-blinded.Rmd", output_format = "bookdown::pdf_document2")
 rmarkdown::render("paper-blinded.Rmd", output_format = "bookdown::html_document2")
 rmarkdown::render("paper-blinded.Rmd", output_format = "bookdown::word_document2")
```
